### 2023-09-03 sections/2-methods.tex
bad recalls
explain frac dim fraction
fix to sharding

With this approach, we begin by taking a random sample of up to 10\% of the data. 
The exact proportion of the dataset in this random sample depends on the dimensionality of the dataset and a user-specified memory limit. 
FIrst, we build a cluster tree on this sample, and 
then consider all clusters at some user-specified depth in the tree. Using the cluster centers 
of these clusters as queries, and a user-specified value of $k$, we perform $k$-NN search using each of the four algorithms described in Section~\ref{subsec:methods:knn-search}. 
We record the 
time taken for each algorithm and select the one which had the lowest total search time over all the queries. 
We then split the rest of the dataset into some user-specified number of shards, and use the algorithm identified in the previous step to perform $k$-NN search on the first shard. 
This search finds the $k$ closest neighbors to the query \emph{in the first shard}. 
We take the furthest of those $k$ neighbors and use its distance from the query as the radius to be used with $\rho$-nearest neighbors search (see Section~\ref{subsec:methods:rnn-search}) on each remaining shard. 
We then take the union of the results of these $\rho$-nearest neighbors searches, along with the $k$ neighbors from the first shard, and then linear search over those points to find the actual $k$ nearest neighbors.

@@

For datasets which \emph{do} fit in memory, we use the same approach to auto-tuning, but with only one shard.

@@

Putting our bounds for coarse and fine search together, we have that $k$-NN by Repeated $\rho$-NN has 
$\mathcal{O}\left(\log_2{\mathcal{N}_{\hat{r_c}}(D)} + k\left(1+ \frac{2\hat{r_c}}{\hat{r}}\left(\frac{k}{\hat{C}}\right)^{\frac{-1}{\hat{d}}}\right)^d\right) = 
\mathcal{O}\left(\log_2{\mathcal{N}_{\hat{r_c}}(D)} + k\left(\frac{2\hat{r_c}}{\hat{r}}\right)^d\left(\frac{k}{\hat{C}}\right)^{\frac{-d}{\hat{d}}}\right)$ 
time complexity, where $\mathcal{N}_{\hat{r_c}}(D)$ is the metric entropy of the dataset, $d$ is the dimensionality of the dataset, and $k$ is the number of nearest neighbors.

>>>>

With this approach, we begin by taking a random sample of up to 10\% of the data. This sample 
is considered the first shard. 
The exact proportion of the dataset in this random sample depends on the dimensionality of the dataset and a user-specified memory limit. 
FIrst, we build a cluster tree on this sample, and 
then consider all clusters at some user-specified depth in the tree. Using the cluster centers 
of these clusters as queries, and a user-specified value of $k$, we perform $k$-NN search using each of the four algorithms described in Section~\ref{subsec:methods:knn-search}. 
We record the 
time taken for each algorithm and select the one which had the lowest total search time over all the queries. 
We then split the rest of the dataset into shards, based on the user-defined memory limit, and use the algorithm identified in the previous step to perform $k$-NN search on the first shard. 
This search finds the $k$ closest neighbors to the query \emph{in the first shard}. 
We take the furthest of those $k$ neighbors and use its distance from the query as the radius to be used with $\rho$-nearest neighbors search (see Section~\ref{subsec:methods:rnn-search}) on each remaining shard.

We then take the union of the results of these $\rho$-nearest neighbors searches, along with the $k$ neighbors from the first shard, and then linear search over those points to find the actual $k$ nearest neighbors.

@@

For datasets which \emph{do} fit in memory, we use the same approach to auto-tuning, but, since the entire remainder of the dataset fits in memory, we use everything 
but that initial 10\% sample as the remaining shard for $\rho$-nearest neighbors search.

@@

Putting our bounds for coarse and fine search together, we have that $k$-NN by Repeated $\rho$-NN has 
$\mathcal{O}\left(\log_2{\mathcal{N}_{\hat{r_c}}(D)} + k\left(1+ \frac{2\hat{r_c}}{\hat{r}}\left(\frac{k}{\hat{C}}\right)^{\frac{-1}{\hat{d}}}\right)^d\right) = 
\mathcal{O}\left(\log_2{\mathcal{N}_{\hat{r_c}}(D)} + k\left(\frac{2\hat{r_c}}{\hat{r}}\right)^d\left(\frac{k}{\hat{C}}\right)^{\frac{-d}{\hat{d}}}\right)$ 
time complexity, where $\mathcal{N}_{\hat{r_c}}(D)$ is the metric entropy of the dataset, $d$ is the dimensionality of the dataset, and $k$ is the number of nearest neighbors. We note that the fraction $\frac{-d}{\hat{d}}$ should, unless fractal dimension is highly variable (that is, local $d$ is quite different from $\hat{d}$), be relatively close to 1.
